Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-03 inspiral_svd.tex
fix dcc and abs
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@932 ccdd05d5-56c1-461a-bf98-85f6876523b4

\begin{abstract}
The rapid detection of compact binary coalescence with a network of advanced
gravitational-wave detectors will offer a unique opportunity for
multi-messenger astronomy.  Prompt detection alerts to the astronomical
community may make it possible to observe the onset of electromagnetic emission
from compact binary coalescence.  We demonstrate a computationally practical
analysis strategy that produces early warning triggers even before
gravitational radiation from the final merger has arrived at the detectors.
With current rate estimates for the Advanced \LIGO{} design configuration, it
should be possible to detect $\sim$10 sources earlier than 10 seconds before
merger in 1 year of live time.
\end{abstract}

@@

This paper has \LIGO\ Document
Number \LIGO-\textsc{p}\oldstylenums{0900004}-v\oldstylenums{3}.}

>>>>

\begin{abstract}
The rapid detection of compact binary coalescence with a network of advanced
gravitational-wave detectors will offer a unique opportunity for
multi-messenger astronomy.  Prompt detection alerts to the astronomical
community may make it possible to observe the onset of electromagnetic emission
from compact binary coalescence.  We demonstrate a computationally practical
analysis strategy that produces early warning triggers even before
gravitational radiation from the final merger has arrived at the detectors.
With current rate estimates for the Advanced \LIGO{} design configuration, it
should be possible to detect $\sim$10 sources earlier than 10 seconds before
merger in 1 year of live time using the method we describe.
\end{abstract}

@@

This paper has \LIGO\ Document
Number \LIGO-\textsc{p}\oldstylenums{0900004}.}
